\textbf{Advection versus diffusion in intraventricular transport}

### 2025-03-26 paper/main.tex
update refs

The numerical solution schemes for the Stokes equations and the
advection-diffusion equation were implemented and solved numerically with
DOLFINx~\cite{dolfinx2023preprint} with petsc4py~\cite{Dalcin2011ParallelPython}
as linear algebra backend. The simulation code is openly
available\fixme{~\cite{zenodo-link-to-all-code}}.
A direct solver using MUMPS~\cite{Amestoy2011Mumps} is used to solve the
linear systems resulting from the discretized Stokes equations.
For the discretized advection-diffusion equation, we use a flexible GMRES solver~\cite{fgmres}
with block Jacobi preconditioning~\cite{Jacobi1845UeberGleichungen} for the outer solves
and ILU preconditioning for the inner solves~\cite{chan1997approximate}. 
We discretize the time-dependent diffusion equation (without advection)
and use the assembled linear system matrix
as the preconditioner matrix for the advection-diffusion problem.
Numerical experiments verified the accuracy of the model implementation
(\Cref{sec:appB_verification}).

@@

%% \textbf{References}\\
%% 1	((Journal articles)) a) A. B. Author 1, C. D. Author 2, Adv. Mater. 2006, 18, 1; b) A. Author 1, B. Author 2, Adv. Funct. Mater. 2006, 16, 1.\\
%% 2	((Work accepted)) A. B. Author 1, C. D. Author 2, Macromol. Rapid Commun., DOI: 10.1002/marc.DOI.\\
%% 3	((Books)) H. R. Allcock, Introduction to Materials Chemistry, Wiley, Hoboken, NJ, USA 2008.\\
%% 4	((Edited books or proceedings volumes)) J. W. Grate, G. C. Frye, in Sensors Update, Vol. 2 (Eds: H. Baltes, W. Göpel, J. Hesse), Wiley-VCH, Weinheim, Germany 1996, Ch. 2.\\
%% 5	((Presentation at a conference, proceeding not published)) Author, presented at Abbrev. Conf. Title, Location of Conference, Date of Conference ((Month, Year)).\\
%% 6	((Thesis)) Author, Degree Thesis, University (location if not obvious), Month, Year.\\
%% 7	((Patents)) a) A. B. Author 1, C. D. Author 2 (Company), Country Patent Number, Year; b) W. Lehmann, H. Rinke (Bayer AG) Ger. 838217, 1952.\\
%% 8	((Website)) Author, Short description or title, URL, accessed: Month, Year.\\
%% 9	…((Please include all authors, and do not use “et al.”))\\

% Table of contents entry should be 50 - 60 words long
% Image should be 55 mm broad and 50 mm high or 110 mm broad and 20 mm high

%% \begin{figure}
%% \textbf{Table of Contents}\\
%% \medskip
%%   \includegraphics{toc-image.png}
%%   \medskip
%%   \caption*{ToC Entry}
%% \end{figure}

>>>>

The numerical solution schemes for the Stokes equations and the
advection-diffusion equation were implemented and solved numerically with
DOLFINx with petsc4py as linear algebra backend
\cite{dolfinx2023preprint, Dalcin2011ParallelPython}.
The simulation code is openly
available\fixme{~\cite{zenodo-link-to-all-code}}.
A direct solver using MUMPS~\cite{Amestoy2011Mumps} is used to solve the
linear systems resulting from the discretized Stokes equations.
For the discretized advection-diffusion equation, we use a flexible GMRES solver
with block Jacobi preconditioning for the outer solves
and ILU preconditioning for the inner solves
\cite{fgmres, Jacobi1845UeberGleichungen, chan1997approximate}. 
We discretize the time-dependent diffusion equation (without advection)
and use the assembled linear system matrix
as the preconditioner matrix for the advection-diffusion problem.
Numerical experiments verified the accuracy of the model implementation
(\Cref{sec:appB_verification}).

@@
